Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/formal.tex
more refs

The definition of |erasef il| is quite important, as it captures the IFC
language's attacker model: elements that are erased cannot be observed
by the attacker.
%
In our case, we assume that the attacker cannot observe sensitive tasks or
messages, or even the number of such entities.
%
While such assumptions are standard~\tocite{}, our definitions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We believe that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniques of~\tocite{}.
  %
  We leave this extension to future work.
}

>>>>

The definition of |erasef il| is quite important, as it captures the IFC
language's attacker model: elements that are erased cannot be observed
by the attacker.
%
In our case, we assume that the attacker cannot observe sensitive tasks or
messages, or even the number of such entities.
%
While such assumptions are standard~\tocite{}, our definitions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We believe that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniques of~\cite{yangresource}.
  %
  We leave this extension to future work.
}
